%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{banking}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}                     % set encoding
\usepackage[scale=0.75]{geometry}               % customize paper
\usepackage[mono=false]{libertine}              % beautiful font
\usepackage[unicode]{hyperref}                  % to use hyperlinks
\usepackage{xcolor}                             % better colors
\usepackage{color}                              % syntactic sugar

% \setlength{\makecvheadnamewidth}{12cm}
\renewcommand*{\namefont}{\fontsize{24}{29}\mdseries\upshape}
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother

% personal data
\firstname{Lester James V.}
\familyname{Miranda}
% \title{Curriculum vit\ae}
\address{Blk. 12 Lot 16, Palmera Northwinds I}{City of San Jose del Monte, Bulacan}
\email{ljvmiranda@gmail.com}
\homepage{ljvmiranda921.github.io}
\mobile{(+63) 926-6481383}
\extrainfo{Currently based in Fukuoka, Japan}


\begin{document}

\maketitle


% EDUCATION ------------------------------------------------------------
\section{Education}
\cventry{2016--2018}
        {M.Eng., Major in Information Architecture}
        {Waseda University}
        {Fukuoka, Japan}{}
        {Furuzuki Neurocomputing Systems}

\cventry{2011--2016}{B.S., Electronics \& Communications Engineering}
        {Ateneo de Manila University}
        {Quezon City, Philippines}
        {\textit{Cum Laude}}
        {Minor in Philosophy}

\cventry{2015}
        {Exchange Student}
        {Institut Catholique d'Arts et M\'etiers}
        {Lille, France}{}
        {7 ECTS credits}

% EXPERIENCE -----------------------------------------------------------
\section{Experience}

\cventry{2017}
        {Research Intern}
        {RIKEN-Advanced Institute for Computational Sciences}
        {Kobe, Japan}{Data Assimilation Research Team}
        {
            \begin{itemize}
                \item Developed...
                \item Studied... 
            \end{itemize}
        }

\cventry{2015}
        {Intern}
        {Manila Electric Company}
        {Pasig, Philippines}{Strategy, Architecture \& Governance}
        {
            \begin{itemize}
                \item Developed use-cases for Big Data and drone automation.
                \item Studied the business impact of Enterprise Mobility in the company.
                \item Presented the results of the study to MERALCO's top executives.
            \end{itemize}
        }

\vspace{0.75em}
\cventry{2015}
        {Intern}
        {Simbahang Lingkod ng Bayan}
        {Quezon City, Philippines}{Disaster Risk Reduction \& Management}
        {
            \begin{itemize}
                \item Assessed the organization's disaster reporting platform, e-Ugnay.
                \item Proposed improvements for platform security and scalability.
            \end{itemize}
        }


% PROJECTS -------------------------------------------------------------
\section{Projects}

\cventry{2017}
        {Owner, https://github.com/ljvmiranda921/pyswarms}
        {PySwarms}{}{}
        {
            \begin{itemize}
                \item Research toolkit for particle swarm optimization written in Python.
                \item Repository can be found at {\color{blue} \httplink[GitHub]{github.com/ljvmiranda921/pyswarms}}, with {\color{blue}\httplink[API documentation]{pyswarms.readthedocs.io/en/latest/}}
            \end{itemize}
        }

\cventry{2017}
        {Collaborator, https://github.com/scikit-multilearn/scikit-multilearn}
        {scikit-multilearn}{}{}
        {
            \begin{itemize}
                \item A scikit-compatible library for multi-label classification in Python
                \item Reorganized unit tests and fixed repository documentation.
            \end{itemize}
        }

% SCHOLARSHIP ----------------------------------------------------------
\section{Scholarships Received}
\cvitem{2016}{Monbugakusho (MEXT) Japanese Government Scholarship}
\cvitem{2015}{French Embassy Government Scholarship}
\cvitem{2011}{Department of Science \& Technology SEI Merit Scholarship}
\cvitem{2011}{Ateneo College Scholarship, 100 Tuition and Fees}

% SKILLS ---------------------------------------------------------------
\section{Skills}

\cvlanguage{Python}{Good working proficiency}{numpy, pandas, scikit-learn, matplotlib, TensorFlow}
\cvlanguage{M. Learning}{Research-level proficiency}{deep unsupervised learning, reinforcement learning, classical ML}
\cvlanguage{Miscellaneous}{Proficient}{UNIX/Linux, \LaTeX, Jekyll, HTML/CSS/Javascript}


% BIBLIOGRAPHY ---------------------------------------------------------
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{publications}

\end{document}


%% end of file `template.tex'.
